\documentclass{resume} % Use the custom resume.cls style
\usepackage[left=0.4 in,top=0.4in,right=0.4 in,bottom=0.4in]{geometry} % Document margins
\newcommand{\tab}[1]{\hspace{.2667\textwidth}\rlap{#1}} 
\newcommand{\itab}[1]{\hspace{0em}\rlap{#1}}
\name{Tharun Vikas SS} % Your name
% You can merge both of these into a single line, if you do not have a website.
\address{+91 9384148359 \\ Erode, Tamil Nadu, India} 
\address{\href{mailto:ssstharunvikas@gmail.com}{G-mail} \\ \href{https://www.linkedin.com/in/tharunvikas55/}{Linkedin} \\ 
\href{https://github.com/Tharunvikas55}{GitHub} \\
\href{https://tharunvikas.vercel.app/}{Portfolio}}  %
\begin{document}
%----------------------------------------------------------------------------------------
%	OBJECTIVE
%----------------------------------------------------------------------------------------
\begin{rSection}{OBJECTIVE}
{Seeking a challenging and dynamic opportunity where I can apply my skills, knowledge, and passion to contribute effectively, grow both personally and professionally, and make a positive impact within a collaborative team environment}
\end{rSection}
%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------
\begin{rSection}{Education}
{\bf Master of Science in Software Systems} \hfill {2020 - current}
\\ CGPA-8.54 / 10 till 7th semester, Kongu Engineering College,Perundurai\\
{\bf Higher Secondary }\hfill {2019 - 2020}\\
85.3 percent, Bharathi Matric Hr Sec school, Vijayamangalam
%{\bf Secondary School}\hfill {2017 - 2018}\\
%87.4 percent, SR Matric Hr Sec school,Uthukuli
\end{rSection}
%------------------------------------------------------------------------------------------
%Experiance
\begin{rSection}{INTENSHIP}
\textbf{Full Stack Developer-AI} \hfill Jan 2024 - current\\
Punchbiz Technologies \hfill \textit{Salem, India} 
    \item Collaborated with the development team to build a web applications,collaborating effectively to contribute to project development.Developed two projects for clients using PHP. 
\end{rSection} 
%----------------------------------------------------------------------------------------
%	WORK EXPERIENCE SECTION
%----------------------------------------------------------------------------------------
\begin{rSection}{PROJECTS}
\vspace{-1.25em}
\item \textbf{Grocery Management System.} {A dynamic Grocery Management System built with Node.js, MongoDB, Express, and EJS enables real-time access to product info, empowering swift and informed decisions. This implementation minimizes waiting times, enhancing operational efficiency effectively.\href{https://github.com/Tharunvikas55/grocery_project_version1}{(Try it here)}}
\item \textbf{Detection Of Monkeypox Disease Using Deep
Learning Techniques.} {A pioneering Research project leverages advanced deep learning models to swiftly identify monkeypox lesions from dermatological images, offering a cutting-edge automated diagnostic approach crucial during outbreaks}
\item \textbf{Vehicle Service Management System.} {Contributed to the Kongu College Hackathon, developing a Vehicle Service Management System web app for streamlined service and maintenance for efficient data handling and performance enhancement.}
\end{rSection} 
%----------------------------------------------------------------------------------------
\begin{rSection}{RESEARCH PAPER} 
\vspace{-1.25em}
    \item \textbf{Detection Of Monkeypox Disease Using Deep Learning Techniques.} {Utilizes deep learning models to detect monkeypox lesions from dermatological images, offering a promising automated solution for timely diagnosis and intervention during outbreaks.}
\end{rSection}
%----------------------------------------------------------------------------------------
%Area of Interest
\begin{rSection}{AREA OF INTEREST}
\begin{tabular}{ @{} >{\bfseries}l @{\hspace{6ex}} l }
Full Stack Development\\
Automation\\
\end{tabular}
\end{rSection}
%----------------------------------------------------------------------------------------
% TECHINICAL STRENGTHS	
%----------------------------------------------------------------------------------------
\begin{rSection}{SKILLS}
\begin{tabular}{ @{} >{\bfseries}l @{\hspace{6ex}} l }
Soft Skills & Teamwork, Time management\\
Programming & C, C++, Java \\
Frontend & HTML, CSS, Tailwind, Javascript, EJS, ReactJs\\
Backend & Node JS, Express JS, MongoDB\\
Tools &  Figma, Git, Postman, Docker, UIPath, Selenium
\end{tabular}
\end{rSection}
%----------------------------------------------------------------------------------------
%Acheivements
\begin{rSection}{Achievements} 
\begin{itemize}
    \item 	2024: Secured 1st place in the Coding-Club Codeathon at Kongu Engineering College
\end{itemize}
\end{rSection}
%--------------------------------------------------------------------------------
%\begin{rSection}{COURSES} 
%\begin{itemize}
%    \item 	Robotic Process Automation 
%    \item	Automation Testing with Selenium
%\end{itemize}
%\end{rSection}
%-----------------------------------------------------------------------------------------
\end{document}
